A Compound Decision Approach to Covariance Matrix Estimation

### 2022-03-15 response_reviews.tex

\item \emph{Page 5, ``that minimizes the compound risk.” $\rightarrow$ “that minimizes an estimate of the compound risk''?}

  Fixed, thanks.

\item \emph{Page 5, after equation 3: Maybe explicitly write that $\beta_S$, $\beta_I$ are scalars (i.e., $\beta_S, \beta_I \in \mathbb{R}$)? Has $\bs{I}$ been explicitly defined as the identity matrix? }

  We have now written that $\beta_S$ and $\beta_I$ are scalars and have identified $\bs{I}$ as the $p \times p$ identity matrix; \textbf{see after equation (3)}.

### 2022-03-15 msg.tex
update QIS, supp

We first explored the consequences of choosing different numbers of cluster centroids in our clustering-based exemplar algorithm described in Section \ref{implementation}. For each model, we generated $n=100$ samples from a $p$-variate $\mathcal{N}(\bs{0}, \bs{\Sigma})$, where $p = 30, 100,$ or $200$. Although $\bb{E}\bs{X}=0$ in our setting, we assume it is unknown and use $\bs{S}=\frac{1}{n-1}(\bs{X}-\bs{\bar{X}})^\top(\bs{X}-\bs{\bar{X}})$. We generated $200$ replicates and reported median errors under the loss function
\begin{equation}
  \label{eq:sim_loss}
  \frac{1}{p} \left\{ \sum_{j,k = 1}^p (\hat{\sigma}_{jk} - \sigma_{jk})^2 \right\}^{1/2},
\end{equation}
where $\hat{\bs{\Sigma}}$ is the estimated matrix with entries $\hat{\sigma}_{jk}$ and $\bs{\Sigma}$ is the true matrix with entries $\sigma_{jk}$. We then fit our proposed method, after positive-definitness correction, for different $K$, where we let $K = rp$ for $r=2,1,0.5,0.25$.

@@

\begin{table}
\begin{center}
\caption{\label{tab:tab1}Median gene expression covariance matrix estimation errors (25\% and 75\% quantiles in parentheses). Bold text highlights the smallest median errors in each column.}
%\setlength{\tabcolsep}{3pt} % Default value: 6pt
\begin{tabular}{rll}
  \Hline
  Brain region & Amygdala & Frontal cortex \\
  \hline
  MSGCor & \textbf{2.26 (1.98, 2.57)} & \textbf{2.3 (2.15, 2.55)} \\
  Adap & 2.6 (2.18, 2.97) & 2.44 (2.18, 2.71) \\
  Linear & 2.3 (2.05, 2.55) & 2.35 (2.19, 2.53)\\
  QIS & 2.61 (2.33, 2.86) & 2.79 (2.64, 2.93)\\
  NERCOME & 2.37 (2.14, 2.62) & \textbf{2.3 (2.14, 2.53)}\\
  CorShrink & \textbf{2.26 (2, 2.56)} & 2.36 (2.2, 2.56)\\
  Sample & 2.61 (2.33, 2.85) & 2.79 (2.64, 2.95)\\
  \hline
\end{tabular}
\end{center}
\end{table}

>>>>

We first explored the consequences of choosing different numbers of cluster centroids in our clustering-based exemplar algorithm described in Section \ref{implementation}. For each model, we generated $n=100$ samples from a $p$-variate $\mathcal{N}(\bs{0}, \bs{\Sigma})$, where $p = 30, 100,$ or $200$. Although $\bb{E}\bs{X}=0$ in our setting, we assume it is unknown and use $\bs{S}=\frac{1}{n-1}(\bs{X}-\bs{\overline{X}})^\top(\bs{X}-\bs{\overline{X}})$. We generated $200$ replicates and reported median errors under the loss function
\begin{equation}
  \label{eq:sim_loss}
  \frac{1}{p} \left\{ \sum_{j,k = 1}^p (\hat{\sigma}_{jk} - \sigma_{jk})^2 \right\}^{1/2},
\end{equation}
where $\hat{\bs{\Sigma}}$ is the estimated matrix with entries $\hat{\sigma}_{jk}$ and $\bs{\Sigma}$ is the true matrix with entries $\sigma_{jk}$. We then fit our proposed method, after positive-definitness correction, for different $K$, where we let $K = rp$ for $r=2,1,0.5,0.25$.

@@

\begin{table}
\begin{center}
\caption{\label{tab:tab1}Median gene expression covariance matrix estimation errors (25\% and 75\% quantiles in parentheses). Bold text highlights the smallest median errors in each column.}
%\setlength{\tabcolsep}{3pt} % Default value: 6pt
\begin{tabular}{rll}
  \Hline
  Brain region & Amygdala & Frontal cortex \\
  \hline
  MSGCor & \textbf{2.26 (1.98, 2.57)} & \textbf{2.3 (2.15, 2.55)} \\
  Adap & 2.6 (2.18, 2.97) & 2.44 (2.18, 2.71) \\
  Linear & 2.3 (2.05, 2.55) & 2.35 (2.19, 2.53)\\
  QIS & 2.48 (2.07, 2.85) & 2.42 (2.18, 2.70)\\
  NERCOME & 2.37 (2.14, 2.62) & \textbf{2.3 (2.14, 2.53)}\\
  CorShrink & \textbf{2.26 (2, 2.56)} & 2.36 (2.2, 2.56)\\
  Sample & 2.61 (2.33, 2.85) & 2.79 (2.64, 2.95)\\
  \hline
\end{tabular}
\end{center}
\end{table}
